UCD\\MSc Thesis Proposal:\\\emph{An Approach To Continuous Capacity Planning In Cloud Environment With Uptime Based Pricing Model}

### 2014-06-30 paper/proposal.tex
wording

New IaaS solutions are becoming available with a growing number of supported pricing models. More often than not, a hosted Cloud environment is used to design and build an infrastructure for a product. The recent availability of different pricing schemes based on resource utilisation and uptime reveals new challenges in already unpredictive capacity planning process. 
When exactly does one pricing scheme becomes more cost effective?

@@

{\bf Motivation.}
\begin{itemize}
\item New startups often attempt to solve globe wide problems and have to either process increasing amounts of data either attract millions of users. Although the problem of scaling is hard enough by itself, the reality with limited budgets requires to tackle the scaling problem from the most optimal, cost-effective angle. Capacity planning can make a difference between making or losing the money in a dynamic, price variable environment. Based on a dynamic nature of business size and external factors like pricing, capacity planning and provisioning need to be continuously adjusted and becomes an integral part of daily operations.
\item Solving the problem of visualisation and optimisation of infrastructure costs will make decisions about pricing scheme and choice of the provider possible in an educated and more confident manner.

>>>>

New IaaS solutions are becoming available with a growing number of supported pricing models. More often than not, a hosted Cloud environment is used to design and build an infrastructure for a product. The recent availability of different pricing schemes based on resource utilisation and uptime reveals new challenges in already unpredictive capacity planning process. One can choose between ad hoc provisioning vs upfront payments and reduced hourly rates. Reserved instances charged upfront are splitted into three groups: light, medium and heavy. Which one is better for a given utilisation model? When exactly does one pricing scheme becomes more cost effective?

@@

{\bf Motivation.}
\begin{itemize}
\item

Capacity planning can make a difference between earning and losing money. Considering a dynamic nature of business and external factors like pricing, capacity planning and provisioning need to be continuously adjusted and become an integral part of daily operations. Having a granual data about infrastructure utilisation is fundamental to make adjustments when it is needed. Frequency of adjustments may vary, however, it is important to have this possibility at any time.
\item Solving the problem of visualisation and optimisation of infrastructure costs will make decisions about pricing scheme and choice of the provider possible in an educated and more confident manner.
